---
title: "[edX] MITx: CTL.SC0x<br>Supply Chain Analytics"
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(simmer)
library(triangle)
library(DT)
```

# Week 7: Building Descriptive Models: Simulation

## Lesson 1: Simulation Basics

### QQ6

What is the quantity of rolls that Suzie should make each day in order to maximize profitability? Assume that the underlying demand ~N(20,5). Round your answer to the closest integer.

```{r}
# set.seed(4)

data_frame(
    production = rep(1:40, each = 1e4),
    demand = rnorm(40e4, 20, 5) %>% round,
    revenue = pmin(production, demand) * 80,
    cost = production * 25,
    profit = revenue - cost
    ) %>%
    group_by(production) %>%
    summarise_each(funs(mean)) %>%
    ggplot(aes(production, profit)) +
    geom_col()
```

## Recitations

### Problem: Boarding Pass Kiosks at Logan

#### Recitation 1.1

1. Create a new model
2. Create a Source for passengers
3. Create a Sink for passengers to exit
4. Specify the length of the simulation
5. Run the model
6. Create a Delay for kiosk use
7. Create a Queue for waiting
8. Run the model
9. Let’s measure time in the queue
10. Run the model

```{r}
customer <-
    create_trajectory("Customer's path") %>%
    seize("Kiosk", 1) %>%
    timeout(function() rtriangle(1, a = 0.5, b = 15, c = 5)) %>%
    release("Kiosk", 1)

logan <-
    simmer("Logan") %>%
    add_resource("Kiosk", 6, 16) %>%
    add_generator("Customer", customer, function() rexp(1, 30/60))
```

Model is run.

```{r}
logan %>% run(until = 9e4)
```

Average times.

```{r}
average_times <- function(m) {
    m %>% get_mon_arrivals(per_resource = TRUE) %>%
        mutate(
            flow_time = end_time - start_time,
            waiting_time = flow_time - activity_time
        ) %>%
        group_by(resource) %>%
        summarise_each(funs(mean), flow_time, activity_time, waiting_time) %>%
        datatable(options = list(dom = 't')) %>% formatRound(2:4, 2)
}
```

```{r}
logan %>% average_times
```

How many passengers made it.

```{r}
resource_popularity <- function(m) {
    m %>% get_mon_arrivals(per_resource = TRUE) %>%
        group_by(name) %>%
        summarise(resource = resource %>% paste(collapse = " -> ")) %>%
        count(resource) %>%
        datatable(options = list(dom = "t"))
}
```

```{r}
logan %>% resource_popularity
```

#### Recitation 1.2

11. Create a Time Plot for queue size
12. Change the queue capacity
13. Run the model
14. Scaling the Time Plot
15. Run the model

Waiting times.

```{r}
logan %>% plot_evolution_arrival_times("waiting_time")
```

Resource usage.

```{r}
logan %>% plot_resource_usage("Kiosk", steps = TRUE)
```

#### Recitation 1.3

16. Create a Resource Pool
17. Replacing the queue with a Seize
18. Add a Release when done
19. Relax capacity at delay
20. Run the model

Resource utilization.

```{r}
logan %>% plot_resource_utilization("Kiosk") +
    geom_label(aes(label = Q50 %>% round(2), y = Q50, x = resource))
```

### Part 2 of Boarding Pass Problem

#### Recitation 1.4

21. Create a Select Output
22. Create a Resource Pool for CSRs
23. Add a Service for seeing the CSRs
24. Let’s measure time in the service
25. Run the model

```{r}
customer <-
    create_trajectory("Customer's path") %>%
    branch(
        option = function() sample(1:2, 1, prob = c(0.8, 0.2)),
        continue = c(F, F),
        create_trajectory("Kiosk path") %>%
            seize("Kiosk", 1) %>%
            timeout(function() rtriangle(1, 0.5, 15, 5)) %>%
            release("Kiosk", 1),
        create_trajectory("CSR path") %>%
            seize("CSR", 1) %>%
            timeout(function() rtriangle(1, 3, 9, 6)) %>%
            release("CSR", 1)
    )

logan <-
    simmer("Logan") %>%
    add_resource("Kiosk", 6, 16) %>%
    add_resource("CSR", 2) %>%
    add_generator("Customer", customer, function() rexp(1, 0.5))
```

Model is run.

```{r}
logan %>% run(until = 9e4)
```

Average times.

```{r}
logan %>% average_times
```

### Part 3a of Boarding Pass Problem

#### Recitation 1.5

26. Define a timeout in the Seize
27. Run the model

```{r}
customer_csr <- create_trajectory("CSR path") %>%
    seize("CSR", 1) %>%
    timeout(function() rtriangle(1, 3, 9, 6)) %>%
    release("CSR", 1)

customer_kiosk <- create_trajectory("Kiosk path") %>%
    renege_in(5, customer_csr) %>%
    seize("Kiosk", 1) %>%
    renege_abort() %>%
    timeout(function() rtriangle(1, 0.5, 15, 5)) %>%
    release("Kiosk", 1)

customer <- create_trajectory("Customer's path") %>%
    branch(
        option = function() sample(1:2, 1, prob = c(0.8, 0.2)),
        continue = c(F, F),
        customer_kiosk,
        customer_csr
    )

logan <-
    simmer("Logan") %>%
    add_resource("Kiosk", 6, 16) %>%
    add_resource("CSR", 2) %>%
    add_generator("Customer", customer, function() rexp(1, 0.5))
```

Model is run.

```{r}
logan %>% run(until = 9e4)
```

How many people benefited from the redirecting technology?

```{r}
# logan %>% get_mon_arrivals %>% count(finished)
logan %>% resource_popularity
```

### Part 3b of Boarding Pass Problem

#### Recitation 1.5

28. Define a timeout in the Service
29. Run the model

```{r}
customer_manager <- create_trajectory("Manager path") %>%
    seize("Manager", 1) %>%
    release("Manager", 1)

customer_csr <- create_trajectory("CSR path") %>%
    renege_in(30, customer_manager) %>%
    seize("CSR", 1) %>%
    renege_abort() %>%
    timeout(function() rtriangle(1, 3, 9, 6)) %>%
    release("CSR", 1)

customer_kiosk <- create_trajectory("Kiosk path") %>%
    renege_in(5, customer_csr) %>%
    seize("Kiosk", 1) %>%
    renege_abort() %>%
    timeout(function() rtriangle(1, 0.5, 15, 5)) %>%
    release("Kiosk", 1)

customer <- create_trajectory("Customer's path") %>%
    branch(
        option = function() sample(1:2, 1, prob = c(0.8, 0.2)),
        continue = c(F, F),
        customer_kiosk,
        customer_csr
    )

logan <-
    simmer("Logan") %>%
    add_resource("Kiosk", 6, 16) %>%
    add_resource("CSR", 1) %>%
    add_resource("Manager", Inf) %>%
    add_generator("Customer", customer, function() rexp(1, 0.5))
```

Model is run.

```{r}
logan %>% run(until = 9e4)
```

How many people asked to talk with a manager?

```{r}
logan %>% resource_popularity
```

### Problem: Patches Beauty Salon

#### Recitation 2.1

```{r}
customer_baths <- create_trajectory() %>%
    seize("Tub", 1) %>%
    seize("Staff", 1) %>%
    timeout(function() rtriangle(1, 5, 15, 10)) %>%
    release("Staff", 1) %>%
    release("Tub", 1)

customer_nails <- create_trajectory() %>%
    seize("Table", 1) %>%
    seize("Staff", 1) %>%
    timeout(function() rtriangle(1, 3, 7, 5)) %>%
    release("Staff", 1) %>%
    release("Table", 1)

customer_dog <- create_trajectory() %>%
    branch(
        option = function() sample(1:2, 1, prob = c(0.7, 0.3)),
        continue = c(F, F), customer_baths, customer_nails
    )

customer_cat <- create_trajectory() %>%
    branch(
        option = function() sample(1:2, 1, prob = c(0.1, 0.9)),
        continue = c(F, F), customer_baths, customer_nails
    )

patches <-
    simmer("Patches") %>%
    add_resource("Staff", 7) %>%
    add_resource("Tub", 4) %>%
    add_resource("Table", 3) %>%
    add_generator("Customer dog", customer_dog, function() rexp(1, 20/60)) %>%
    add_generator("Customer cat", customer_cat, function() rexp(1, 20/60))
```

Model is run.

```{r}
patches %>% run(until = 70000)
```

What is the utilization of:

a) the staff?
b) the tubs?
c) the tables?

```{r}
patches %>% plot_resource_utilization(c("Staff", "Tub", "Table")) +
    geom_label(aes(label = Q50 %>% round(2), y = Q50, x = resource))
```

What is the average time required (incl. waiting in line) for:

a) a beauty bath?
b) having your nails polished?

```{r}
patches %>% average_times
```

### Patches Beauty Salon, Revisited

#### Recitation 2.2

```{r}
customer_baths <- create_trajectory() %>%
    seize("Tub", 1) %>%
    seize("Staff", 1) %>%
    timeout(function() rnorm(1, 10, 3)) %>%
    release("Staff", 1) %>%
    release("Tub", 1)

customer_nails <- create_trajectory() %>%
    seize("Table", 1) %>%
    seize("Staff", 1) %>%
    timeout(function() runif(1, 3, 7)) %>%
    release("Staff", 1) %>%
    release("Table", 1)

customer_dog <- create_trajectory() %>%
    branch(
        option = function() sample(1:2, 1, prob = c(0.7, 0.3)),
        continue = c(F, F), customer_baths, customer_nails
    )

customer_cat <- create_trajectory() %>%
    branch(
        option = function() sample(1:2, 1, prob = c(0.1, 0.9)),
        continue = c(F, F), customer_baths, customer_nails
    )

patches <-
    simmer("Patches") %>%
    add_resource("Staff", 7) %>%
    add_resource("Tub", 4) %>%
    add_resource("Table", 3) %>%
    add_generator("Customer dog", customer_dog, function() rexp(1, 20/60)) %>%
    add_generator("Customer cat", customer_cat, function() rexp(1, 20/60))
```

Model is run.

```{r}
patches %>% run(until = 70000)
```

What is the utilization of:

a) the staff?
b) the tubs?
c) the tables?

```{r}
patches %>% plot_resource_utilization(c("Staff", "Tub", "Table")) +
    geom_label(aes(label = Q50 %>% round(2), y = Q50, x = resource))
```

What is the average time required (incl. waiting in line) for:

a) a beauty bath?
b) having your nails polished?

```{r}
patches %>% average_times
```
