---
title: "[edX] MITx: CTL.SC0x<br>Supply Chain Analytics"
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(simmer)
library(triangle)
```

# Week 7: Building Descriptive Models: Simulation

## Lesson 1: Simulation Basics

### QQ6

What is the quantity of rolls that Suzie should make each day in order to maximize profitability? Assume that the underlying demand ~N(20,5). Round your answer to the closest integer.

```{r}
# set.seed(4)

data_frame(
    production = rep(1:40, each = 1e4),
    demand = rnorm(40e4, 20, 5) %>% round,
    revenue = pmin(production, demand) * 80,
    cost = production * 25,
    profit = revenue - cost
    ) %>%
    group_by(production) %>%
    summarise_each(funs(mean)) %>%
    ggplot(aes(production, profit)) +
    geom_col()
```

## Recitations

### Problem: Boarding Pass Kiosks at Logan

#### Recitation 1.1

1. Create a new model
2. Create a Source for passengers
3. Create a Sink for passengers to exit
4. Specify the length of the simulation
5. Run the model
6. Create a Delay for kiosk use
7. Create a Queue for waiting
8. Run the model
9. Let’s measure time in the queue
10. Run the model

```{r}
customer <-
    create_trajectory("Customer's path") %>%
    seize("Kiosk", 1) %>%
    timeout(function() rtriangle(1, a = 0.5, b = 15, c = 5)) %>%
    release("Kiosk", 1)

logan <-
    simmer("Logan") %>%
    add_resource("Kiosk", 6, 16) %>%
    add_generator("Customer", customer, function() rexp(1, 30/60))
```

Model is run.

```{r}
logan %>% run(until = 9e4)
```

Average times.

```{r}
logan %>% get_mon_arrivals %>%
    mutate(flow_time = end_time - start_time, waiting_time = flow_time - activity_time) %>%
    summarise_each(funs(mean), flow_time, activity_time, waiting_time) %>%
    knitr::kable
```

How many passengers made it.

```{r}
logan %>% get_mon_arrivals %>%
    mutate(flow_time = end_time - start_time, waiting_time = flow_time - activity_time) %>%
    count(finished) %>%
    knitr::kable
```

#### Recitation 1.2

11. Create a Time Plot for queue size
12. Change the queue capacity
13. Run the model
14. Scaling the Time Plot
15. Run the model

Waiting times.

```{r}
logan %>% plot_evolution_arrival_times("waiting_time")
```

Resource usage.

```{r}
logan %>% plot_resource_usage("Kiosk", steps = TRUE)
```

#### Recitation 1.3

16. Create a Resource Pool
17. Replacing the queue with a Seize
18. Add a Release when done
19. Relax capacity at delay
20. Run the model

Resource utilization.

```{r}
logan %>% plot_resource_utilization("Kiosk") +
    geom_label(aes(label = Q50 %>% round(2), y = Q50, x = resource))
```

### Part 2 of Boarding Pass Problem

#### Recitation 1.4

21. Create a Select Output
22. Create a Resource Pool for CSRs
23. Add a Service for seeing the CSRs
24. Let’s measure time in the service
25. Run the model

```{r}
customer <-
    create_trajectory("Customer's path") %>%
    branch(
        option = function() sample(1:2, 1, prob = c(0.8, 0.2)),
        continue = c(F, F),
        create_trajectory("Kiosk path") %>%
            seize("Kiosk", 1) %>%
            timeout(function() rtriangle(1, 0.5, 15, 5)) %>%
            release("Kiosk", 1),
        create_trajectory("CSR path") %>%
            seize("CSR", 1) %>%
            timeout(function() rtriangle(1, 3, 9, 6)) %>%
            release("CSR", 1)
    )

logan <-
    simmer("Logan") %>%
    add_resource("Kiosk", 6, 16) %>%
    add_resource("CSR", 2) %>%
    add_generator("Customer", customer, function() rexp(1, 0.5))
```

Model is run.

```{r}
logan %>% run(until = 9e4)
```

Average times.

```{r}
logan %>% get_mon_arrivals(per_resource = TRUE) %>%
    mutate(flow_time = end_time - start_time, waiting_time = flow_time - activity_time) %>%
    group_by(resource) %>%
    summarise_each(funs(mean), flow_time, activity_time, waiting_time) %>%
    knitr::kable
```

### Part 3a of Boarding Pass Problem

#### Recitation 1.5

26. Define a timeout in the Seize
27. Run the model

```{r}
customer_csr <- create_trajectory("CSR path") %>%
    seize("CSR", 1) %>%
    timeout(function() rtriangle(1, 3, 9, 6)) %>%
    release("CSR", 1)

customer_kiosk <- create_trajectory("Kiosk path") %>%
    renege_in(5, customer_csr) %>%
    seize("Kiosk", 1) %>%
    renege_abort() %>%
    timeout(function() rtriangle(1, 0.5, 15, 5)) %>%
    release("Kiosk", 1)

customer <- create_trajectory("Customer's path") %>%
    branch(
        option = function() sample(1:2, 1, prob = c(0.8, 0.2)),
        continue = c(F, F),
        customer_kiosk,
        customer_csr
    )

logan <-
    simmer("Logan") %>%
    add_resource("Kiosk", 6, 16) %>%
    add_resource("CSR", 2) %>%
    add_generator("Customer", customer, function() rexp(1, 0.5))
```

Model is run.

```{r}
logan %>% run(until = 9e4)
```

How many people benefited from the redirecting technology?

```{r}
logan %>% get_mon_arrivals(per_resource = TRUE) %>%
    mutate(
        flow_time = end_time - start_time,
        waiting_time = flow_time - activity_time
    ) %>%
    spread(resource, replication) %>%
    group_by(name) %>%
    summarise_each(
        funs(sum(., na.rm = TRUE)),
        flow_time, activity_time, waiting_time, CSR, Kiosk
    ) %>%
    with(., table(CSR, Kiosk)) %>%
    knitr::kable
```

### Part 3b of Boarding Pass Problem

28. Define a timeout in the Service
29. Run the model
